---
title: "Flight delay"
author: "Alessia De Biase"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

In this file we try to predict the delay of each flight using the `ridgereg()` function from the package `lab7ab`.

```{r include=FALSE}
library(devtools)
library(caret)
library(nycflights13)
library(dplyr)
install_github("brbatv/lab7",force=TRUE)
library(lab7ab)
```

## Cleaning "weather" and "flights" datasets:

Exploring the dataset from `nycflights13` library.

The dataset weather has the following variables: 

```{r echo=FALSE,warning=FALSE}
colnames(weather)
```

The dataset flights has the following variables:

```{r echo=FALSE,warning=FALSE}
colnames(flights)
```

The two datasets have some common variable such as: `year`,`month`, `day`, `origin`, `hour`, `time_hour` so a new dataset is created by adding extra informations to the `flights` dataset. 

```{r echo=FALSE,warning=FALSE}
flights_weather <- left_join(flights, weather,by = c("year", "month", "day", "origin", "hour", "time_hour"))
```

The weather variables are interesting to be selected for the prediction so the `database` has been created with the added columns:

```{r warning=FALSE}
database <- select(flights_weather,month,day, sched_dep_time,sched_arr_time, dep_delay, arr_delay,temp,dewp,wind_dir, wind_speed,wind_gust,precip,pressure,visib)
```

## Data partition: test, train and validation

To use the `caret` package all the missing values need to be taked off from the database. 
The data, at this point, have been splitted into three new dataset: 

\itemize{

\item *train* 80% of the observations
\item *test* 5% of the observations
\item *validation* 15% of the observations

}

```{r warning=FALSE}
library(caret)
set.seed(3456)
database<-na.omit(database)

trainIndex = createDataPartition(database$arr_delay, 
                       p=0.8, list=FALSE,times=1)
train = database[trainIndex,]
notrain = database[-trainIndex,]
validationIndex = createDataPartition(notrain$arr_delay, 
                       p=0.75, list=FALSE,times=1)
validation=database[validationIndex,]

test = notrain[-validationIndex,]
```

## Training Ridge Regression

Training on the train dataset the best value obtained for `lambda` is $10^{8}$.

```{r warning=FALSE}
#root mean squared arror
rmse <- function(error){
    sqrt(mean(error^2))
}

#formula for ridge regression
formula=arr_delay~month+day+sched_dep_time+sched_arr_time+dep_delay+temp+dewp+wind_dir+ wind_speed+wind_gust+precip+pressure+visib 

#training ridge regression for different values of lambda
mod<-ridgereg$new(formula=formula, data=train,lambda=10^8)

Y_validation<-validation$arr_delay
Y_predicted <- mod$predict(datanew=validation)

#calculating the error
error= Y_predicted - Y_validation


RMSE_check<-rmse(error)
```

## Best Lambda found for the predicted model

The best lambda has been found, with it the test set has been predicted and the RMSE of the predicted model is:

```{r echo=FALSE,warning=FALSE}

best_lambda=10^8

mod<-ridgereg$new(formula=formula, data=train,lambda=best_lambda)  
  
Y_test<-test$arr_delay
Y_predicted2 <- mod$predict(datanew=test)

error2= Y_predicted2 - Y_test

RMSE_best_lambda<-rmse(error2)
RMSE_best_lambda
```
