---
title: "RC class for ridge regression"
author: "Bruno Barakat"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

The lab7ab package provides a RC class named `ridgereg` to apply ridge regression.


```{r,include=FALSE}
library(devtools)
install_github("brbatv/lab7",force=TRUE)
library(lab7ab)
library(MASS)
library(mlbench)
library(caret)
library(leaps)
data("BostonHousing")
```

## Splitting the data
After loading the BostonHousing data frame, we will partitionize it in two parts. 

```{r}
training_data <- createDataPartition(BostonHousing$crim,p = 0.55)

training <- BostonHousing[training_data$Resample1, ]
test <- BostonHousing[-training_data$Resample1, ]
```


## Select best model by choosing variables
We now need to select the best variables to predict crim.

```{r,results:hide}
set.seed(27)
full_model <- lm(crim~.,data=training)

```
```{r,include=FALSE}
set.seed(27)
step <- stepAIC(full_model, direction="backward")
```

```{r,eval=FALSE,warning=FALSE}

step <- stepAIC(full_model, direction="backward")
```

```{r,warning=FALSE}
step$anova # display results 
```
The backward method used in stepAIC gave us a model with the lowest AIC :  `crim ~ zn + rm + dis + rad + medv`

```{r,warning=FALSE}
lm1 <- caret::train(crim ~ ., data=training, method = 'leapForward')
lm1
summary(lm1)
```

The leapForward method gave us a model with only two variables `crim ~

## Using our own model in train function from caret package
```{r}
ridgeex <- list(type="Regression", 
              library="lab7ab",
              loop=NULL,
              prob=NULL,
              parameters=data.frame(parameter="lambda",class="numeric",label="lambda"),
              grid=function(y,x, len=NULL, search="grid")
              {
                data.frame(lambda=c(0.1,0.5,1,2))
              },
              fit=function (x, y, wts, param, lev, last, classProbs, ...) 
              {
                dat <- if (is.data.frame(x)) 
                  x
                else as.data.frame(x)
                dat$.outcome <- y
                out <- ridgereg$new(formula=.outcome ~ ., data = dat, lambda=param$lambda, ...)
                out
              },
              predict = function (modelFit, newdata, submodels = NULL,preProc=NULL) 
              { 
                if (!is.data.frame(newdata)) 
                  newdata <- as.data.frame(newdata)
                
                modelFit$predict(newdata)
              })


Ridgereg_model <- list(
    type = c("Regression"),
    library = "lab7ab",
    loop = NULL,
    prob = NULL)

Ridgereg_model$parameters <- data.frame(parameter = "lambda",
                                        class = "numeric",
                                        label = "lambda")

Ridgereg_model$grid <- function (x, y, len = NULL, search = "grid"){
    data.frame(lambda = seq(0,2,by=0.25))
}

Ridgereg_model$fit <- function (x, y, wts, param, lev, last, classProbs, ...){
    dat <- if (is.data.frame(x))
        x
    else
        as.data.frame(x)
    dat$outcome <- y
    
    output <-
        ridgereg$new(outcome ~ ., data = dat, lambda = param$lambda, ...)
    
    output
}


Ridgereg_model$predict <- function(modelFit, newdata, preProc = NULL, submodels = NULL){
    if (!is.data.frame(newdata))
        newdata <- as.data.frame(newdata)
    modelFit$predict(newdata)
}

testo<-caret::train(crim ~ zn + rm + dis + rad + medv, data=training, method = Ridgereg_model)
#testo
```

